\documentclass[10pt]{article}
\usepackage[margin=0.7in]{geometry}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\pagenumbering{gobble}

\begin{document}

%==================== HEADER ====================
\begin{center}
{\LARGE \textbf{Vishnu Kondaveeti}} \\[4pt]
Software Engineer | AI Systems | Backend Development \\[4pt]
\href{mailto:vishnuchowdary.kondaveeti@gmail.com}{vishnuchowdary.kondaveeti@gmail.com} ;|;
+91-94920-74736 ;|;
\href{https://www.linkedin.com/in/vishnu-kondaveeti-7856502b4}{LinkedIn} ;|;
\href{https://github.com/VishnuKondaveeti}{GitHub}
\end{center}

%==================== SUMMARY ====================
\section*{Professional Summary}

Software engineering student specializing in backend systems and AI-driven platforms.
Experienced in building scalable APIs, automation workflows, and data-driven applications using Python and Java.
Strong foundation in data analytics, machine learning, and distributed systems with hands-on experience in
LLM orchestration, RAG pipelines, and analytics workflows. Passionate about designing scalable and intelligent
software systems that generate actionable insights from data.

%==================== SKILLS ====================
\section*{Technical Skills}

\begin{itemize}[leftmargin=*, itemsep=2pt]

\item \textbf{Programming Languages:}
Python, Java, SQL

\item \textbf{Data Analytics:}
Python Data Analysis (Pandas, NumPy), Data Cleaning, Data Transformation,
Exploratory Data Analysis (EDA), Statistical Analysis, Data Visualization

\item \textbf{AI Systems:}
Large Language Models (Google Gemini, Llama, DeepSeek-R1), Retrieval-Augmented Generation (RAG),
LangChain, LangGraph, Multi-Agent Systems, Prompt Engineering, Embeddings,
Semantic Search, Vector Databases (ChromaDB)

\item \textbf{Backend Development:}
FastAPI, REST APIs, Microservices Architecture, Async Programming,
Webhooks, API Documentation (OpenAPI / Swagger)

\item \textbf{Machine Learning:}
Regression, Classification, Clustering, Feature Engineering,
Model Evaluation, Cross Validation

\item \textbf{Data Processing & ETL:}
Pandas, NumPy, Data Cleaning, Data Transformation,
ETL Pipelines, Exploratory Data Analysis

\item \textbf{Cloud & DevOps:}
Microsoft Azure, Docker, GitHub Actions, Containerization, CI/CD, Linux CLI

\item \textbf{Core Computer Science:}
Data Structures & Algorithms, Operating Systems, DBMS, Computer Networks

\item \textbf{Tools:}
Git, Docker, Maven, Postman, Jupyter Notebook, n8n, VS Code

\end{itemize}

%==================== PROJECTS ====================
\section*{Projects}

\textbf{Agentic RAG Pipeline} \hfill \textit{Python, FastAPI, LangChain, ChromaDB, Ollama, DeepSeek-R1}

\begin{itemize}[leftmargin=*, itemsep=2pt]
\item Developed a full-stack Agentic RAG system with a FastAPI backend and interactive Vanilla JS frontend for real-time document querying.
\item Implemented complex routing logic to dynamically decide between context-aware retrieval and direct LLM generation using local DeepSeek-R1 models.
\item Integrated sentence-transformers (all-MiniLM-L6-v2) for semantic document indexing and high-precision vector search in ChromaDB.
\item Automated document ingestion pipelines for multi-page PDFs with recursive text splitting and asynchronous processing.
\item Visualized agent "thinking" processes (routing decisions and source citations) in a responsive, low-latency web dashboard.
\end{itemize}

\textbf{Autonomous Multi-Agent AI Research Platform} \hfill \textit{Python, FastAPI, RAG, Google Gemini, n8n}

\begin{itemize}[leftmargin=*, itemsep=2pt]
\item Architected an end-to-end research platform integrating Google Gemini with RAG pipelines for automated literature analysis.
\item Built an n8n-driven automation workflow triggered via FastAPI webhooks to orchestrate paper collection, processing, and reporting.
\item Developed specialized agents (Research, Retrieval, Analysis, Advisor) using the Orchestrator pattern for complex task management.
\item Implemented document ingestion pipelines with ChromaDB vector store indexing research documents for semantic retrieval.
\item Developed analytics pipelines to identify research trends and generate insights from collected datasets.
\item Designed modular architecture separating ingestion, retrieval, analysis, and orchestration layers.
\end{itemize}

\textbf{Lead Generation Automation System} \hfill \textit{n8n, Webhooks, Google Sheets API, SMTP}

\begin{itemize}[leftmargin=*, itemsep=2pt]
\item Developed an automated lead capture and management workflow using n8n.
\item Implemented webhook-based triggers to collect leads from web forms.
\item Automated storage of lead data into Google Sheets for centralized tracking.
\item Configured email notifications to alert sales teams in real-time for incoming leads.
\item Performed data analysis on captured leads to identify patterns and generate campaign insights.
\end{itemize}

\textbf{Multi-Agent System Using LangGraph} \hfill \textit{Python, LangGraph, LangChain}

\begin{itemize}[leftmargin=*, itemsep=2pt]
\item Developed a graph-based multi-agent workflow with shared state and structured task orchestration.
\item Implemented specialized Researcher and Writer agents for automated content generation.
\item Designed scalable agent communication workflows.
\end{itemize}

\textbf{Real-Time Object Detection System} \hfill \textit{Python, YOLO, OpenCV}

\begin{itemize}[leftmargin=*, itemsep=2pt]
\item Built a real-time object detection pipeline for live video streams.
\item Processed and analyzed image datasets for training and evaluation.
\item Applied preprocessing and augmentation techniques to improve model performance.
\item Optimized inference pipeline to enable low-latency real-time predictions.
\end{itemize}

\textbf{Book My Game – Slot Booking Platform} \hfill \textit{Java, Spring MVC, MySQL}

\begin{itemize}[leftmargin=*, itemsep=2pt]
\item Designed a backend system for court slot booking using Java and Spring MVC.
\item Implemented concurrency-safe booking logic preventing double booking.
\item Designed relational database schema and optimized queries using MySQL.
\item Built modular service-layer architecture ensuring maintainability and scalability.
\end{itemize}

%==================== ACHIEVEMENTS ====================
\section*{Achievements}

\textbf{AI Research Automation Hackathon} \hfill \textit{2025}

\begin{itemize}[leftmargin=*, itemsep=2pt]
\item Qualified for Round 2 using an Autonomous Multi-Agent AI Research Platform.
\item Built an AI platform capable of automated literature retrieval, analysis, and summarization.
\item Demonstrated multi-agent orchestration and RAG-based knowledge retrieval workflows.
\end{itemize}

%==================== EXPERIENCE ====================
\section*{Experience}

\textbf{AI \& Cloud Virtual Intern | IBM SkillsBuild} \hfill \textit{Sept 2025 -- Oct 2025}

\begin{itemize}[leftmargin=*, itemsep=2pt]
\item Worked on machine learning pipelines including data preprocessing, model training, and evaluation.
\item Explored cloud-based AI workflows and scalable model deployment.
\end{itemize}

\textbf{AI \& Data Analytics Virtual Intern | Shell} \hfill \textit{Oct 2025 -- Nov 2025}

\begin{itemize}[leftmargin=*, itemsep=2pt]
\item Conducted exploratory data analysis to identify trends and insights in datasets.
\item Cleaned and transformed raw data using Python to prepare it for machine learning models.
\item Evaluated model performance using statistical metrics and validation techniques.
\end{itemize}

%==================== EDUCATION ====================
\section*{Education}

\textbf{Vellore Institute of Technology (VIT-AP)}, India \hfill \textit{2022 -- 2027}

Integrated M.Tech in Computer Science \& Engineering — \textbf{CGPA: 8.91 / 10.0}

\textbf{Relevant Coursework:} Data Structures, Algorithms, Operating Systems, DBMS, Computer Networks, Machine Learning

\vspace{4pt}

\textbf{Narayana Junior College}, Hyderabad \hfill \textit{2020 -- 2022}

Intermediate (MPC) — Score: 98\%

\vspace{4pt}

\textbf{St. Ann’s High School}, Bhadrachalam \hfill \textit{2020}

ICSE — Score: 86\%

%==================== CERTIFICATIONS ====================
\section*{Certifications}

\begin{itemize}[leftmargin=*, itemsep=2pt]

\item \textbf{IBM SkillsBuild}
\begin{itemize}
\item Introduction to Artificial Intelligence
\item Introduction to Generative AI
\item Machine Learning
\item Deep Learning
\end{itemize}

\item \textbf{Additional Certifications}
\begin{itemize}
\item Natural Language Processing (NLP)
\item Computer Vision
\item AI \& Cloud Virtual Internship – IBM SkillsBuild
\item AI \& Data Analytics Virtual Internship – Shell
\item Oracle Cloud Infrastructure DevOps Professional – Oracle
\end{itemize}

\end{itemize}

\end{document}
